%\section{Suggestions}
%
%\subsection{Do not use a self-signed CA certificate}
%
%Trusted root certificates on the Internet have very strict protection measures, such as offline protection.But users may store the seif-signed CA's private key on the local computer, and may even be exposed on the Internet, such as send by email. This will greatly Increase the risk of CA private key disclosure. The attacker can obtain a fake certificate that is completely legal and extremely difficult to distinguish for the user. The only difference between the attacker and the real certificate may be that the public key, the serial number and the signature value are different and difficult to be discovered. In this case, the possibility of being attacked is very high. We recommend not issuing a CA certificate when using a self-signed certificate.
%
%We did not find a way to directly add a endpoint certificate to Firefox's certificate store(Section 5.2). So try to avoid using self-signed certificates in Firefox browser.
%
%\subsection{Minimize the validity period of the certificate}
%For personal websites, the revoked certificate is not detected by Chrome(section 5.3), and Chrome is one of the most popular browsers. A workable approach is to minimize the validity of the certificate and update the certificate regularly.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and Suggestion}
%In the experiment, we found that different browsers have different processing methods for some unsafe scenarios.
%Through comparison between them, we have summarized the existing risks of several browsers.

In this section,
    we present some suggestions to reduce browser defects on handling HTTPS errors.

\subsection{Weak Cryptographic Algorithm}
Edge and IE should gradually stop accepting certificates signed by MD5 or SHA-1, 
    and display Level-B warnings on MD5 and SHA-1.
\subsection{Certificate Revocation}
Chrome checks the revocation status
    generally through CRLSet \cite{CRLSet} that covers only 0.35\% of all revocations in the Internet \cite{liu2015end}.
Chrome should collect more revoked certificates that belong to popular websites, 
    since they will impact the largest fraction of Internet.

\subsection{Certificate Extension}
%\textbf{Basic Constraints.}
The Basic Constraints extension is defined to distinguish CA certificates and non-CA ones \cite{cooper2008rfc5280}.
However,
    when the server certificate is verified by a certificate in which the cA flag is false,
    i.e., a non-CA entity acts as CAs to sign server certificates
        for any domain names to launch attacks,
            Firefox shows only bypassable Level-B warnings.
Moreover, Firefox does not process the pathLenConstraint field correctly,
    and the violated pathLenConstraint does not trigger warnings.
These defects can be exploited to launch successful MitM and impersonation attacks on Firefox.

If a CA acts as the TLS server in HTTPS,
    i.e., the cA flag in the ``server'' certificate is true,
Chrome, Edge and IE consider it as secure and show no warning.
However, %in our opinion,
    such configurations are rather uncommon,
    and Level-A warnings shall be suitable.

%\textbf{Extended Key Usage and Key Usage.}
If a certificate contains the extensions of Key Usage and Extended Key Usage,
    two extensions must be processed independently,
    and the certificate is only used for the purpose(s) consistent with both extensions  \cite{cooper2008rfc5280}.
%If there is no purpose consistent with both extensions, then the certificate MUST NOT be used for any purpose \cite{cooper2008rfc5280}.
This rule is not complied with in Chrome, Edge and IE:
    when the server certificate includes only the keyCertSign usage and the serverAuth extended usage,
     no warning is shown.
%
Chrome, Edge, and IE do not process the Key Usage extension correctly,
    even if it is marked as critical:
no warning is shown when the TLS server certificate does not include the keyEncipherment usage.
%However,
%    these browsers process the \emph{non-critical} Extended Key Usage extension correctly:
%    when the server certificate does not include the serverAuth extended usage,
%    Level-C warnings are shown.
So a certificate for other purposes may be maliciously used in HTTPS, and accepted by these browsers.

% If a certificate contains both a key usage extension and an extended
%   key usage extension, then both extensions MUST be processed
 %  independently and the certificate MUST only be used for a purpose
  % consistent with both extensions.  If there is no purpose consistent
   %with both extensions, then the certificate MUST NOT be used for any
   %purpose.(RFC 5280)
\subsection{Name Validation}

All browsers show bypassable Level-B warnings on different name validation errors:
complete mismatch,
WWW mismatch and out-of-wildcard-scope subdomain.
However,
%    in our opinion,
    these errors bring very different levels of risk,
    and it is practicable to show a higher-level warning on complete mismatch
     because low-cost TLS server certificates are available.


%The CA/Browser Forum suggests that
%    deprecates the CN field and lists applicable names in SAN field.
The browsers behave inconsistently in name validation.
Chrome checks the domain name \emph{only} in the SAN extension.
Firefox, Edge, and IE consider a server certificate as secure,
    if it contains correct CN but no SAN;
    on the contrary, it triggers Level-B warnings in Chrome.
This may lead to a problem of usability:
    a legitimate certificate considered as secure by other browsers,
    may trigger a warning in Chrome.



\subsection{HSTS}
%HSTS is supported by all evaluated browsers.
The visits over plain HTTP that definitely violates the HSTS policy,
 trigger only Level-A warnings, not interrupting the user's browsing.
If the HSTS policy is enforced by the pre-loaded list, which is manually configured by the user,
    the user shall be explicitly notified on such visits over HTTP.
If HSTS is enforced  by the HSTS header, which is sent by the website,
    such visits over plain HTTP are probably initiated by attackers because the website itself does not allow HTTP visits.

\subsection{HPKP}
HPKP is supported only in Chrome and Firefox.
        Chrome and Firefox do not conduct HPKP validation
            when the certificate chain is verified by a user-installed root CA certificate.
So a website cannot enhance its HTTPS security by HPKP,
    unless it applies for a certificate from the publicly-trusted CAs.
 %   Thus, If a malware installs its root certificate on the user's computer,
 %       it may defeat the protections of HPKP and successfully launch the man-in-the-middle attack.

%To enable certificate chain validation, Chrome has access to two stores of trust anchors: certificates that are empowered as issuers. One trust anchor store is the system or public trust anchor store, and the other other is the local or private trust anchor store. The public store is provided as part of the operating system, and intended to authenticate public internet servers. The private store contains certificates installed by the user or the administrator of the client machine. Private intranet servers should authenticate themselves with certificates issued by a private trust anchor.

%Chrome does not perform pin validation when the certificate chain chains up to a private trust anchor. A key result of this policy is that private trust anchors can be used to proxy (or MITM) connections, even to pinned sites. ¡°Data loss prevention¡± appliances, firewalls, content filters, and malware can use this feature to defeat the protections of key pinning.
% We deem this acceptable because the proxy or MITM can only be effective if the client machine has already been configured to trust the proxy¡¯s issuing certificate ¡ª that is, the client is already under the control of the person who controls the proxy (e.g. the enterprise¡¯s IT administrator). If the client does not trust the private trust anchor, the proxy¡¯s attempt to mediate the connection will fail as it should.

%In order to control the browsing behavior of the internal network, some companies often pre-set the self-signed certificate in the computer in the office area, and replace the HTTPS connection certificate in the gateway to obtain the information contained in the HTTPS traffic, detect and prevent the information leakage inside the company, which is a typical MITM attack. Some malware may also use the same way to attack a personal computer. Many computer applications will trigger the UAC of the Windows system during installation. After clicking and agreeing, the computer settings can be modified. After the malware spoofs the user's consent, you can modify the computer settings, such as burying your own root certificate. Eavesdrop on all traffic through a self-signed certificate and send sensitive information to the attacker.

